---
title: "``inspectdf::inspect_imb``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(inspectdf)
library(magrittr)
library(dplyr)
```


#### Description
Summarise and compare columnwise imbalance for non-numeric columns in one or two dataframes.

#### Usage

<pre><code>
  inspect_imb(df1, df2 = NULL, show_plot = FALSE, include_na = FALSE)
</code></pre>
  
#### Arguments
  
* ``df1``: A data frame
* ``df2``: An optional second data frame for comparing columnwise imbalance. Defaults to NULL.
* ``show_plot``: (Deprecated) Logical flag indicating whether a plot should be shown. Superseded by the function``show_plot()`` and will be dropped in a future version.
* ``include_na``: Logical flag, whether to include missing values as a unique level. Default is
FALSE - to ignore NAs.

#### Details

When a single data frame is specified, a tibble is returned which contains columnwise imbalance,
with columns

*  ``col_name`` character vector containing column names of df1.
*  ``value`` character vector containing the most common categorical level in each column of df1.
*  ``pcnt`` the percentage of each column's entries occupied by the level in value column.
*  ``cnt`` the number of occurrences of the most common categorical level in each column of df1.


When both df1 and df2 are specified, the most common levels in df1 are compared to columns in df2. If a categorical column appears in both dataframes, a simple test is performed to test the null hypothesis that the rate of occurrence of the common level in df1 is the same in both dataframes.

The resulting tibble has columns

*  ``col_name`` character vector containing column names of df1 and df2.
*  ``value`` character vector containing the most common categorical level in each column of df1.
*  ``pcnt_`` the percentage of each column's entries occupied by the level in value column.
*  ``cnt_`` the number of occurrences of the most common categorical level in each column of df1 and df2.

#### Value

A tibble summarising and comparing the imbalance for each non-numeric column in one or a pair
of data frames.

#### Examples 

```{r}
data("starwars", package = "dplyr")
# get tibble of most common levels
inspect_imb(starwars)
# compare imbalance
inspect_imb(starwars, starwars[1:10, -3])
```

