---
title: "``inspectdf::inspect_types``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(inspectdf)
library(magrittr)
library(dplyr)
```

#### Description

Summarise and compare column types in one or two dataframes.

#### Usage

<pre><code>
inspect_types(df1, df2 = NULL, show_plot = FALSE)
</code></pre>

#### Arguments

* ``df1``: A data frame.
* ``df2``: An optional second data frame for comparison.
* ``show_plot``: (Deprecated) Logical flag indicating whether a plot should be shown. Superseded by the function ``show_plot()`` and will be dropped in a future version.




#### Examples 

```{r}
inspect_types(iris)
```

```{r}
inspect_types(mtcars)
```

```{r}
data("starwars", package = "dplyr")
# get tibble of column types for the starwars data
inspect_types(starwars)
# compare two data frames
inspect_types(starwars, starwars[, -1])
````


#### Details

When df2 = NULL, a tibble is returned with the columns

*  ``type``: character vector containing the column types in df1.
*  ``cnt`` integer counts of each type.
*  ``pcnt``: the percentage of all columns with each type.
*  ``col_name``: the names of columns with each type.

When a second data frame df2 is specified, column type summaries are tabulated for both data
frames to enable comparison of contents. The resulting tibble has the columns

*  ``type``: character vector containing the column types in df1 and df2.
*  ``cnt_1``, ``cnt_2``: pair of integer columns containing counts of each type - in each of df1 and df2.
*  ``pcnt_1``, ``pcnt_2``: pair of columns containing the percentage of columns with each type - the data frame name are appended.

#### Value

A tibble summarising the count and percentage of different column types for one or a pair of data frames.