---
title: "``inspectdf::inspect_mem``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(inspectdf)
library(magrittr)
library(dplyr)
```

#### Description

Summarise and compare the memory usage in one or two dataframes.

#### Usage
<pre><code>
inspect_mem(df1, df2 = NULL, show_plot = FALSE)
</code></pre>

#### Arguments

* ``df1``: A data frame.
* ``df2``: An optional second data frame for comparing column sizes. Defaults to NULL.
* ``show_plot``: (Deprecated) Logical flag indicating whether a plot should be shown. Superseded by the function ``show_plot()`` and will be dropped in a future version.

#### Details

When a single data frame is specified, a tibble is returned which contains columnwise memory
usage in descending order of size:

*  ``col_name``: character vector containing column names of df1.
*  ``size``: character vector containing memory usage of each column.
*  ``pcnt``: the percentage of total memory usage used by each column.

When both df1 and df2 are specified, column sizes are jointly tabulated for both data frames, by performing a full join by ``col_name``. 
Rows are sorted in descending order of size as they appear in df1:

*  ``col_name``: character vector containing column names of df1 and df2.
*  ``size_1``, ``size_2``: character vector containing memory usage of each column in each of df1 and df2.
*  ``pcnt_1``, ``pcnt_2``: the percentage of total memory usage of each column within each of df1 and df2.

#### Value

A tibble summarising and comparing the columnwise memory usage for one or a pair of data frames.

#### Examples 

````{r}
data("starwars", package = "dplyr")
# get tibble of column memory usage for the starwars data
inspect_mem(starwars)
# compare memory usage
inspect_mem(starwars, starwars[1:10, -3])
```