---
title: "``inspectdf::inspect_cat``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(inspectdf)
library(magrittr)
library(dplyr)
```


inspect_cat Summarise and compare the levels within each categorical feature in
one or two dataframes.

#### Description

Summarise and compare the levels within each categorical feature in one or two dataframes.

#### Usage
<pre><code>
inspect_cat(df1, df2 = NULL, show_plot = FALSE)
</code></pre>

#### Arguments
* ``df1``: A dataframe
* ``df2``: An optional second data frame for comparing categorical levels. Defaults to
NULL.
* ``show_plot``: (Deprecated) Logical flag indicating whether a plot should be shown. Superseded by the function ``show_plot()`` and will be dropped in a future version.

#### Details

When only df1 is specified, a tibble is returned which contains summaries of the categorical levels in df1.

*  ``col_name``: character vector containing column names of df1.
*  ``cnt`` integer column containing count of unique levels found in each column (including NA).
*  ``common character``: column containing the name of the most common level.
*  ``common_pcnt``: percentage of each column occupied by the most common level shown in common.
*  ``levels``: relative frequency of levels in each column.

When both df1 and df2 are specified, the relative frequencies of levels across columns common both dataframes are compared. 
In particular, the population stability index, and Fisher's exact test
are performed as part of the comparison.

*  ``col_name``: character vector containing column names of df1 and df2.
*  ``jsd``: numeric column containing the Jensen-Shannon divergence. This measures the difference
in distribution of a pair of categorical features. Values near to 0 indicate agreement of the distributions, while 1 indicates disagreement.
*  ``fisher_p``: p-value corresponding to Fisher's exact test. A small p indicates evidence that the two sets of relative frequencies are actually different.
*  ``lvls_1``, ``lvls_2``: relative frequency of levels in each of df1 and df2.

#### Value

A tibble summarising and comparing the categorical features in one or a pair of data frames.

#### Examples 

```{r}
data("starwars", package = "dplyr")
inspect_cat(starwars)
# compare the levels in two data frames
inspect_cat(starwars, starwars[1:20, ])
```