---
title: "``inspectdf::inspect_num``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(inspectdf)
library(magrittr)
library(dplyr)
```


#### Description
Summarise and compare the numeric variables within one or two dataframes

#### Usage
<pre><code>
inspect_num(df1, df2 = NULL, breaks = 20, breakseq = NULL,
            show_plot = FALSE)
</code><pre>

#### Arguments

* ``df1``: A data frame
* ``df2``: An optional second data frame for comparing categorical levels. Defaults to NULL.
* ``breaks``: Optional argument determining how breaks are constructed for histograms when comparing numeric data frame features. This is passed to
* ``breakseq``: For internal use only. Argument that accepts a pre-specified set of break points, default is NULL.
* ``show_plot``: (Deprecated) Logical flag indicating whether a plot should be shown. Superseded by the function ``show_plot()`` and will be dropped in a future version.
 - ``hist(..., breaks)``. See ?hist for more details.



#### Examples 
```{r}
data("starwars", package = "dplyr")
# show summary statistics for starwars
inspect_num(starwars)
# with a visualisation too - try to limit number of bins
inspect_num(starwars, breaks = 10)
# compare two data frames
inspect_num(starwars, starwars[-c(1:10), ], breaks = 10)
```

#### Details

If only df1 is specified, inspect_num returns a tibble with columns
*  ``col_name``: character vector containing the column names in df1 and df2
*  min, q1, median, mean, q3, max and sd: the minimum, lower quartile, median, mean, upper
quartile, maximum and standard deviation for each numeric column.
*  ``pcnt_na``: the percentage of each numeric feature that is missing
*  hist a list of tibbles containing the relative frequency of values in a set of discrete bins for
each column.

If both df1 and df2 are specified, the tibble has columns

*  ``col_name``: character vector containing the column names in df1 and df2
*  ``hist_1``,`` hist_2``: list column for histograms of each of df1 and df2. Where a column appears in both dataframe, the bins used for df1 are reused to calculate histograms for df2.
*  ``jsd``: numeric column containing the Jensen-Shannon divergence. This measures the difference in distribution of a pair of binned numeric features. Values near to 0 indicate agreement of the distributions, while 1 indicates disagreement.
*  ``fisher_p``: p-value corresponding to Fisher's exact test. A small p indicates evidence that the two histograms are actually different.

#### Value
A tibble containing statistical summaries of the numeric columns of df1, or comparing the histograms
of df1 and df2.
