---
title: "``inspectdf::inspect_cor``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(inspectdf)
library(magrittr)
library(dplyr)
```

#### Description

Summarise and compare Pearson's correlation coefficients for numeric columns in one or two dataframes.

#### Usage
<pre><code>
  inspect_cor(df1, df2 = NULL, with_col = NULL, alpha = 0.05,  show_plot = FALSE)
</code></pre>
  
#### Arguments

* ``df1``: A data frame
* ``df2``: An optional second data frame for comparing correlation coefficients. Defaults to NULL.
* ``with_col``: Character vector of columns to calculate correlations with. When set to the default, NULL, all pairs of correlations are returned.
* ``alpha``: Alpha level for correlation confidence intervals. Defaults to 0.05.
* ``show_plot``: (Deprecated) Logical flag indicating whether a plot should be shown. 
 - Superseded by the function ``show_plot()`` and will be dropped in a future version.



#### Examples 

```{r}
data("starwars", package = "dplyr")
# correlations in numeric columns
inspect_cor(starwars)
```


```{r}
# only show correlations with 'mass' column
inspect_cor(starwars, with_col = "mass")
```

```{r}
# compare correlations with a different data frame
inspect_cor(starwars, starwars[1:10, ])
```

#### Details

When only df1 is specified, a tibble is returned which contains correlation coefficients 

*  ``col_1``, ``co1_2``: character vectors containing names of numeric columns in df1.
*  ``corr``: numeric values of Pearson's correlation coefficient.
*  ``lower``, ``upper```: lower and upper values of the confidence interval for the correlations.
*  ``p_value``: p-value associated with the null hypothesis of 0 correlation, small values indicate evidence that the true correlation is not equal to 0.

When both df1 and df2 are specified, the tibble returned performs a comparison of the correlation coefficients across the dataframes.

*  ``col_1``, ``co1_2`` character vectors containing names of numeric columns in either df1 or df2.
*  ``corr_1``, ``corr_2`` numeric values of Pearson's correlation coefficient observed in df1 and df2, respectively.
*  ``p_value``: p-value associated with the null hypothesis that the two correlation coefficients are the same. Small values indicate that the true correlation coefficients differ between the two dataframes.

#### Value
A tibble summarising and comparing the correlations for each numeric column in one or a pair of
data frames.