---
title: "``inspectdf::inspect_na ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(inspectdf)
library(magrittr)
library(dplyr)
```

#### Description

Summarise and compare the rate of missingness in one or two dataframes.

#### Usage

<pre><code>
  inspect_na(df1, df2 = NULL, show_plot = FALSE)
</code></pre>
  
#### Arguments

* ``df1``: A data frame
* ``df2``: An optional second data frame for making columnwise comparison of missingness. Defaults to NULL.
* ``show_plot``: (Deprecated) Logical flag indicating whether a plot should be shown. Superseded by the function ``show_plot()`` and will be dropped in a future version.

#### Details

When a single data frame is specified, the a tibble is returned which contains the count and percentage
of missing values, with column names

*  ``col_name``: character vector containing column names of df1.
*  ``cnt`` integer vector containing the number of missing values by column.
*  ``pcnt``: the percentage of each column with missing values

When both df1 and df2 are specified, missingness is compared across columns occurring in both data frames. A test of the null hypothesis that the rate of missingness is the same across the same column in either dataframe.

*  ``col_name`` the name of the columns occurring in either df1
*  ``cnt_1``, ``cnt_2`` pair of integer vectors containing counts of missing entries for each column in df1 and df2.
*  ``pcnt_1``, ``pcnt_2`` pair of columns containing percentage of missing entries for each column in df1 and df2.
*  ``p_value``: p-value associated with test of the rates of missingness. Small values indicate evidence that the rate of missingness differs for a column occurring in both df1 and df2.

#### Value

A tibble summarising the count and percentage of columnwise missingness for one or a pair of data
frames.

#### Examples 

```{r}
data("starwars", package = "dplyr")
# inspect missingness in starwars data
inspect_na(starwars)
# compare two dataframes
inspect_na(starwars, starwars[1:30, ])
```