---
title: "``inspectdf::show_plot``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(inspectdf)
library(magrittr)
library(dplyr)
```

#### Description

Visualise summaries and comparisons of one or two dataframes.

#### Usage

<pre><code>
show_plot(x, text_labels = TRUE, alpha = 0.05, high_cardinality = 0,
            plot_layout = NULL, col_palette = 0)
</code></pre>
  
#### Arguments

* ``x``: Dataframe resulting from a call to an 'inspect_' function.
* ``text_labelsx``: Whether to show text annotation on plots (when show_plot = T).
* ``alphax``: Alpha level for performing significance tests. Defaults to 0.05.
* ``high_cardinalityx``:
Minimum number of occurrences of category to be shown as a distinct segment
in the plot (inspect_cat only). Default is 0. This can help when some columns
contain many unique or near-unique levels that take a long time to render.
* ``plot_layoutx``: Vector specifying the number of rows and columns in the plotting grid. For
example, 3 rows and 2 columns would be specified as ``plot_layout = c(3, 2)``.
Default is TRUE.

#### Palette 

``col_palette`` Integer indicating the colour palette to use.

* '0': (default) 'ggplot2' color palette 
* '1': a [colorblind friendly palette](http://www.cookbookr.com/Graphs/Colors_(ggplot2)/) 
* '2': [80s theme](https://www.color-hex.com/colorpalette/25888) 
* '3': [rainbox theme](https://www.color-hex.com/color-palette/79261)
* '4': [mario theme](https://www.color-hex.com/color-palette/78663) 
* '5': [pokemon theme](https://www.color-hex.com/color-palette/78664)

#### Examples 

```{r}
# Load 'starwars' data
data("starwars", package = "dplyr")
# categorical plot
x <-inspect_cat(starwars)
show_plot(x)
```

```{r}
x <-inspect_cat(starwars)
show_plot(x,col_palette=1)
```

```{r}
# correlations in numeric columns
x <-inspect_cor(starwars)
show_plot(x)
```


```{r}
# feature imbalance bar plot
x <-inspect_imb(starwars)
show_plot(x)
```


```{r}
# memory usage barplot
x <-inspect_mem(starwars)
show_plot(x)
```


```{r}
# missingness barplot
x <-inspect_na(starwars)
show_plot(x)
```


```{r}
# histograms for numeric columns
x <-inspect_num(starwars)
show_plot(x)
```


```{r}
# barplot of column types
x <-inspect_types(starwars)
show_plot(x)
```