---
title: "``groupedstats::grouped_slr``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(VIM)
```

#### Description

Function to run simple linear regression (slr) on multiple variables across multiple grouping variables.

#### Usage
<pre><code>

grouped_slr(data, dep.vars, indep.vars, grouping.vars)

</code></pre>
#### Arguments 

* ``data``: Dataframe from which variables are to be taken.
* ``dep.vars``: List criterion or dependent variables for simple linear model ( y in y ~ x ).
* ``indep.vars``: List predictor or independent variables for simple linear model ( x in y ~ x ).
* ``grouping.vars``: List of grouping variables.

#### Examples
```{r}

# another possibility
groupedstats::grouped_summary(
  data = datasets::iris,
  grouping.vars = Species,
  measures = Sepal.Length:Petal.Width,
  measures.type = "numeric" 
  )
# if you have just one variable per argument, you need not use `c()`

groupedstats::grouped_summary(
  data = datasets::ToothGrowth,
  grouping.vars = supp,
  measures = len,
  measures.type = "numeric"
  )
```

#### Value
A  tibble  dataframe  with  tidy  results  from  simple  linear  regression  analyses.   The  estimates  are
standardized, i.e. the lm model used is scale(y) ~ scale(x) , and not y ~ x
.

#### Author(s)
Indrajeet Patil

