---
title: "grouped_ggdotplotstats"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggstatstplots)
```



Grouped histograms for distribution of a labelled numeric variable

#### Description
Helper function for ggstatsplot::ggdotplotstats to apply this function across multiple levels
of a given factor and combining the resulting plots using ``ggstatsplot::combine_plots``.

#### Usage
<pre><code>

grouped_ggdotplotstats(data, x, y, grouping.var, title.prefix = "Group",
xlab = NULL, ylab = NULL, subtitle = NULL, caption = NULL,
type = "parametric", test.value = 0, bf.prior = 0.707,
bf.message = FALSE, robust.estimator = "onestep",
conf.level = 0.95, nboot = 500, k = 2,
ggtheme = ggplot2::theme_bw(), ggstatsplot.layer = TRUE,
point.color = "black", point.size = 3, point.shape = 16,
results.subtitle = TRUE, centrality.para = "mean",
centrality.color = "blue", centrality.size = 1,
centrality.linetype = "dashed", centrality.line.labeller = TRUE,
centrality.k = 2, test.value.line = FALSE,
test.value.color = "black", test.value.size = 1,
test.value.linetype = "dashed", test.line.labeller = TRUE,
test.k = 0, messages = TRUE, ...)

</code></pre>
#### Arguments

* ``data`` :   Dataframe from which variables specified are preferentially to be taken. This
argument is optional.
* ``x``: A numeric variable.
* ``y``: Label or grouping variable.
* grouping.var Grouping variable.
* ``title.prefix``: Character specifying the prefix text for the fixed plot title (name of each factor
level) (Default: "Group").
* `` xlab`` :    Label for x axis variable.
* ``ylab`` :   Label for y axis variable.
* ``subtitle`` :   The text for the plot subtitle. Will work only if results.subtitle = FALSE.
* ``caption``:  The text for the plot caption.
* ``type`` :   Type of statistic expected ("parametric" or "nonparametric" or "robust" or "bayes").Corresponding abbreviations are also accepted: "p" (for parametric),
"np" (nonparametric), "r" (robust), or "bf"resp.
* ``test.value``: A number specifying the value of the null hypothesis (Default: 0).

#### Examples

```{n}

set.seed(123)
# creating a dataframe with summary
(df_summarized <-
    groupedstats::grouped_summary(
      data = ggstatsplot::intent_morality,
      grouping.vars = c(condition, harm),
      measures = rating
    ))
```
```{r}
# plot
ggstatsplot::grouped_ggdotplotstats(
  data = df_summarized,
  x = mean,
  y = harm,
  grouping.var = condition,
  xlab = "moral judgment (average)",
  ylab = "type of harm",
  title.prefix = "intentional status",
  point.color = "red",
  point.shape = 18,
  point.size = 5,
  centrality.para = FALSE
)
```

#### Additional Arguments
* ``bf.prior`` :  bf.prior A number between 0.5 and 2 (default 0.707), the prior width to use in calculating
Bayes factors.
* ``bf.message``:   Logical that decides whether to display Bayes Factor in favor of the null hypothesis
for parametric test (Default: FALSE).
* ``robust.estimator``:
If test = "robust" robust estimator to be used ("onestep" (Default), "mom",
or "median"). For more, see ?WRS2::onesampb.
conf.level A scalar value between 0 and 1. If unspecified, the default is to return 95% lower
and upper confidence intervals (0.95).
nboot Number of bootstrap samples for robust one-sample location test (Default: 100).
* ``k``: Number of digits after decimal point (should be an integer) (Default: k = 2).
* ``ggtheme``: A function, ggplot2 theme name. Default value is ggplot2::theme_bw().
Any of the ggplot2 themes, or themes from extension packages are allowed
(e.g., ggthemes::theme_economist(), hrbrthemes::theme_ipsum_ps(), ggthemes::theme_fivethirtyeight(),
etc.).
* ``ggstatsplot.layer``:
Logical that decides whether theme_ggstatsplot theme elements are to be
displayed along with the selected ggtheme (Default: TRUE).
point.color Character describing color for the point (Default: "black").
point.size Numeric specifying size for the point (Default: 3).
point.shape Numeric specifying shape to draw the points (Default: 16 (a dot)).
* ``results.subtitle``:
Decides whether the results of statistical tests are to be displayed as a subtitle
(Default: TRUE). If set to FALSE, only the plot will be returned.
* ``centrality.para``:
Decides which measure of central tendency ("mean" or "median") is to be displayed
as a vertical line.
centrality.color
Decides color for the vertical line for centrality parameter (Default: "blue").
* ``centrality.size``:
Decides size for the vertical line for centrality parameter (Default: 1.2).
centrality.linetype
Decides linetype for the vertical line for centrality parameter (Default: "dashed").
centrality.line.labeller
A logical that decides whether line labels should be displayed for the centrality.
para line (Default: TRUE).
grouped_ggdotplotstats 53
centrality.k Integer denoting the number of decimal places expected for centrality parameter
label. (Default: 2).
* ``test.value.line``:
Decides whether test value is to be displayed as a vertical line (Default: FALSE).
test.value.color
Decides color for the vertical line denoting test value (Default: "black").
* ``test.value.size``:
Decides size for the vertical line for test value (Default: 1.2).
test.value.linetype
Decides linetype for the vertical line for test value (Default: "dashed").
test.line.labeller
A logical that decides whether line labels should be displayed for test.value line
(Default: TRUE).
test.k Integer denoting the number of decimal places expected for test.value label.
(Default: 0 ).
messages Decides whether messages references, notes, and warnings are to be displayed
(Default: TRUE).
* ``...`` :  ArXguments passed on to combine_plots
title.text String or plotmath expression to be drawn as title for the combined
plot.
title.color Text color for title.
title.size Point size of title text.
title.vjust Vertical justification for title. Default = 0.5 (centered on y). 0 =
baseline at y, 1 = ascender at y.
title.hjust Horizontal justification for title. Default = 0.5 (centered on x). 0 =
flush-left at x, 1 = flush-right.
title.fontface The font face ("plain", "bold" (default), "italic", "bold.italic")
for title.
* ``caption.text``:   String or plotmath expression to be drawn as the caption for the
combined plot.
* ``caption.color``:    Text color for caption.
* ``caption.size``:  Point size of title text.
* ``caption.vjust``:   Vertical justification for caption. Default = 0.5 (centered on y).
0 = baseline at y, 1 = ascender at y.
* ``caption.hjust ``:   Horizontal justification for caption. Default = 0.5 (centered on
x). 0 = flush-left at x, 1 = flush-right.
* ``caption.fontface  ``:  The font face ("plain" (default), "bold", "italic", "bold.italic")
for caption.
* ``sub.text  ``:   The label with which the combined plot should be annotated. Can be
a plotmath expression.
* ``sub.color  ``:    Text color for annotation label (Default: "black").
* ``sub.size`` : Point size of annotation text (Default: 12).
* ``sub.x`` :   The x position of annotation label (Default: 0.5).
* ``sub.y`` :   The y position of annotation label (Default: 0.5).
54 grouped_ggdotplotstats
* ``sub.hjust`` :    Horizontal justification for annotation label (Default: 0.5).
* ``sub.vjust`` :   Vertical justification for annotation label (Default: 0.5).
* ``sub.vpadding`` :   Vertical padding. The total vertical space added to the label,
given in grid units. By default, this is added equally above and below the label.
However, by changing the y and vjust parameters, this can be changed
(Default: grid::unit(1, "lines")).
* ``sub.fontface ``: The font face ("plain" (default), "bold", "italic", "bold.italic")
for the annotation label.
* ``sub.angle ``:  Angle at which annotation label is to be drawn (Default: 0).
* ``sub.lineheight ``:   Line height of annotation label.
title.caption.rel.heights Numerical vector of relative columns heights while combining (title, plot, caption).
title.rel.heights Numerical vector of relative columns heights while combining (title, plot).
caption.rel.heights Numerical vector of relative columns heights while combining (plot, caption).

#### Author(s)
Indrajeet Patil
See Also
ggdotplotstats

