---
title: "``groupedstats::signif_column``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(groupedstats)
```

## ``groupedstats::signif_column()``

Creating a new character type column with significance labels

#### Description

This function will add a new column to a dataframe containing p-values

#### Usage
<pre><code>

signif_column(data = NULL, p, messages = FALSE)

</code></pre>
#### Arguments 

* ``data``: Data frame from which variables specified are preferentially to be taken.
* ``p``: The column containing p-values.
* ``messages``: Logical decides whether to produce notes (Default:TRUE).


#### Examples
```{r}

# vector as input
groupedstats::signif_column(p = c(0.05, 0.1, 1, 0.00001, 0.001, 0.01))
# dataframe as input
# preparing a newdataframe
df <- cbind.data.frame(
  x = 1:5,
  y = 1,
  p.value = c(0.1, 0.5, 0.00001, 0.05, 0.01)
  )
groupedstats::signif_column(data = df, p = p.value)
# numbers entered as characters are also tolerated
groupedstats::signif_column(p = c("1", "0.1", "0.0002", "0.03", "0.65"))
```
#### Value
Returns the originally entered object (either a vector or a dataframe) in tibble format with an additional column corresponding to statistical significance.

#### Author(s)
Indrajeet Patil
