---
title: "``groupedstats::specify_decimal_p``"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(VIM)
```
## ``specify_decimal_p``

Custom function for getting specified number of decimal places in results for p-value

#### Description

Function to format an R object for pretty printing with a specified (k ) number of decimal places. The function also allows really small p -values to be denoted as "``p < 0.001``" rather than "``p = 0.000``" . 

Note that if ``p.value`` is set to TRUE , the minimum value of k allowed is 3 . If k is set to less than 3, the function will ignore entered k value and use k = 3 instead.

#### Usage

<pre><code>

specify_decimal_p(x, k = 3, p.value = FALSE)

</code></pre>

#### Arguments 

* ``x``: A numeric variable.
* ``k``: Number of digits after decimal point (should be an integer) (Default: k = 3).
* ``p.value``: Decides whether the number is a p-value (Default: FALSE).
* ``Value``: Formatted numeric values.


#### Examples
```{r}

groupedstats::specify_decimal_p(x = 0.00001, k = 2, p.value = TRUE)
groupedstats::specify_decimal_p(x = 0.008, k = 2, p.value = TRUE)
groupedstats::specify_decimal_p(x = 0.008, k = 3, p.value = FALSE)
```

#### Author(s)

Indrajeet Patil
